---
title: "W_UP_01"
author: "David Acevedo"
date: "fall 2024"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
boxplot(pushups~position,data=mydata)
```

the line players have less pushups than the skilled players by atleast 20 pushups.

## Numerical Descrtiptive results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
favstats(pushups~position,data=mydata)
```
so the median shows that the skilled players have at least a 33 difference than the line players showing that the line players are less likely to do more push ups than the skilled players  


## Inferential  results 

```{r}
t.test(pushups~position,data=mydata)
```
the probability we get is p-value 0.000009421 i think the skill players are doing a lot more pushups than the line players  



i grabbed the code from the helper files for my graphical data. i edited the code to "my data" so the program can get the data from my files to input into the program, and with that it made a graph that showed the difference between skilled players and line players, the graph had at least a tiny difference from the skilled players and the line players because the skilled players had at least 20 more push ups then the line players, then i took the same code and used it for the  






